Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2016-04-15 writeup/gz_hubble_data.tex
Description of user weights from @bamford. Closes #40.

\subsection{User weighting}\label{ssec:weighting}
The votes of individual users who classified galaxies in GZH are combined to make a vote fraction for each question on the classification tree. Users' votes are weighted slightly \citep[in a method identical to that described in][]{wil13} such that users who frequently disagree with all other users end up having very low weights. The majority of users have weights very close to $w=1.0$

{\note STEVEN: Is this true for GZH - do you have a plot of the distribution of user weights or consistencies we can include here?}.

>>>>

\subsection{User weighting}\label{ssec:weighting}
The votes of individual users who classified galaxies in GZH are combined to make a vote fraction for each question on the classification tree. Users' votes are weighted slightly \citep[in a method identical to that described in][]{wil13} such that users who frequently disagree with all other users end up having very low weights. The user weighting $w$ is 1 for the top 95\% of users as ranked by consistency. For the bottom 5\% of users, $w$ drops smoothly and is effectively zero for only the bottom 1\% of classifiers in the CDF. The overall effect on the GZH dataset is relatively small, but this method is effective at filtering out contributions from random or delibrately malicious classifiers.
